---
title: "pted_week5_rexercise"
format: html
---

## Preparation

```{r}
library("readr")
library("sf")
library("terra")
library("dplyr")
library("lubridate")
library("ggplot2")
library("tmap")

wildschwein_BE <- read_delim("wildschwein_BE_2056.csv", ",") |>
    st_as_sf(coords = c("E", "N"), crs = 2056, remove = FALSE)
```

## Task 1: Import and visualize spatial data

```{r}
feldaufnahme <- read_sf("Feldaufnahmen_Fanel.gpkg")
```

-   What information does the dataset contain?

    -   FieldID, Frucht and geom

-   What is the geometry type of the dataset (possible types are: Point, Lines and Polygons)?

    -   Polygon

-   What are the data types of the other columns?

    -   Numeric (FieldID) and Character (Frucht)

-   What is the coordinate system of the dataset?

    -   CH1903+ / LV95


## Task 2: Annotate Trajectories from vector data

```{r}
# Filter data
start_date <- "2015-05-01"
end_date <- "2015-06-30"

wildschwein_filtered <- wildschwein_BE |> 
  filter(DatetimeUTC >= as.POSIXct(start_date, tz = "UTC"),
         DatetimeUTC <= as.POSIXct(end_date, tz = "UTC"))

# Join data
wildschwein_joined <- st_join(wildschwein_filtered, feldaufnahme)
```

